Signatures of Foreground Sky in Power Spectra of Redshifted Neutral Hydrogen from the Epoch of Reionization

### 2014-09-07 foreground_delay_spectrum_modeling.tex

\subsection{Data Analysis}\label{sec:data-analysis}

The data are flagged for interference \citep{off12,off10}, removing $\sim 3$\% of the data. These are averaged in time and frequency to 2s and 40kHz respectively.

\subsection{Imaging and deconvolution}\label{sec:FHD}

{\bf Describe the FHD data analysis up to the point of getting calibrated visibilities here.}

@@

We obtain the delay spectrum of these calibrated visibilities using equation~\ref{eqn:delay-transform} while choosing $W'_f(f)$ to be a {\it Blackman--Harris} window function. Due to periodic gaps in frequency bandpass occurring in intervals of 1.28~MHz (see figure~\ref{fig:bandpass}), the delay spectrum is expected to contain harmonics of actual foreground emission repeated at intervals of 0.78~$\mu$s. Hence, we have employed deconvolution by {\it CLEAN} algorithm \citep{tay99} along the delay axis \citep{par09,par12} to rid the delay spectra of such artifacts. The convolving kernel for the algorithm is given by the inverse Fourier transform of the instrumental bandpass shape.

>>>>

\subsubsection{Initial Data processing}\label{sec:data-analysis}
The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off12,off10}, removing 3\% of the data and averaged in time  and frequency from the raw 1/2s,40kHz to 2s, 80khz. These data are then calibrated to a simulation of the sky containing 2420 point sources selected from the MWA Commissioning Survey (N.H Walker, in prep).  MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning. It has a flux limit of 25~mJy and a the declination range of -12\arcdeg to -40\arcdeg evenly covering the field of view of the observations reported here.        The calibration sources are selected to fall within the 5\% primary lobe of the tile beam. The calibration algorithm computes a per channel, per antenna, complex gain solutions averaged to two minute intervals.  The solutions are still fairly low signal to noise so we iteratively project along the antenna and frequency dimensions to capture the relatively independent passband and antenna to antenna variation. First we average the channel gains over all antenna to obtain a high signal to noise measurement of the bandpass.  After applying this single passband, we do a second round of calibration and fit a 2nd order amplitude and first order phase for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variation in cable delay. Finally we fit for an additional phase known to be caused by reflection in 150m cables. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

We obtain the delay spectrum of these calibrated visibilities taking the delay transform of each baseline's spectrum (equation~\ref{eqn:delay-transform}) choosing $W'_f(f)$ to be a {\it Blackman--Harris} window function. The spectrum is multiplied by  the additional weight of the flagged channels which occur rarely for interference and at at regular spacing every 1.28~MHz where the edges of coarse channels are known to have a slight aliasing effect.  In delay space, these weights translate into a convolution by a ringing harmonic point spread function (PSF).  We deconvolve this PSF using a one dimensional CLEAN algorithm \citep{tay99} as described for the delay axis by \citet{par09,par12}. The CLEAN procedure iteratively finds and subtracts peak values convolved by the Fourier transform of the weights.   We limit the selection of peaks to modes inside the delay horizon corresponding to smooth spectrum sources on the sky --ie beneath the black line in Figure \ref{fig:fhd_data}.
